Checklist

### 2019-05-08 presentations/2019-04-27_shutdown/checklist.tex
[presentation/2019-04-27_shutdown] Finish checklist

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\subsection{Computers}
\DevDef{Radio computer [3]}{
  \textbf{Lv2}\\
}

@@

\onecolumn
\Person{Jessie}{
  Equipments and power supplies are mostly located between the machine table and the 1.5 table.
}
\begin{center}
  {\LARGE\textbf{Equipment list}}
\end{center}
\begin{longtable}{|c|c|c|}
  \hline
  \textbf{ID}&\textbf{Equipment}&\textbf{Location}\\\hline
  \multicolumn{3}{|c|}{\textbf{Machine table Facing the wall} north}\\\hline
  1&Benchtop power 2chn&Lv2\\\hline
  2&Home power (24)&Lv2 above 1.0 tweezer breadboard\\\hline
  3&Home power ($\pm$15,5)&Lv2 above home power (24)\\\hline
  4&Benchtop power x9 (2chn x3)&Lv2 next to home power (24) and ($\pm$15,5)\\\hline
  5&Current servo for compensation coil&Lv1 below home power (24)\\\hline
  6&Kenneth servo for 1.0 Cs tweezer&Lv1\\\hline
  7&High voltage Amp for 630 lock&Lv1\\\hline
  8&Vincent servo x2 for STIRAP lasers&Lv1\\\hline
  9&Greiner servo for 1.0 Na tweezer&Lv1 above Vincent servos\\\hline
  10&Rack for STRAP&Lv1 next to Vincent servos\\\hline
  11&Till driver v2 x2 for STIRAP lasers&Lv1 above rack for 1.5\\\hline
  12&Temp servo x3 for STIRAP&Lv2 next to 9x benchtop power\\\hline
  13&FPGA box for 1.5&Lv2\\\hline
  14&Home power ($\pm$15,5)&Lv2 next to FPGA box\\\hline
  15&Benchtop power x2&Lv2 on home power ($\pm$15,5)\\\hline
  16&Benchtop power&Lv2 next to home power ($\pm$15,5)\\\hline
  17&Benchtop power x2 (2chn x1)&Floor rack Lv1\\\hline
  18&Till driver v2 x2 for 1.5 Cs Raman&Floor rack Lv2\\\hline
  19&Kenneth servo for 1.5 Cs Raman phase lock&Floor rack Lv2 above Till drivers\\\hline
  20&Benchtop power&Floor rack Lv2 next to Till drivers\\\hline
  21&Temp servo x2 for 1.5 Cs Raman&Floor rack Lv2\\\hline
  22&Piezo driver for 1.5 Cs Raman&Floor rack Lv2 above home temp servos\\\hline
  23&Delay generator for 1.5 Na&Lv1 below 1.5 output panel\\\hline
  24&Till driver v2 for 1.0 Innolume&Lv1 next to delay generator\\\hline
  25&Kenneth servo for 1.5 tweezers&Lv1\\\hline
  26&Temp servo for 1.0 Innolume&Lv1\\\hline
  27&Shutter driver&Lv1 on M2 controller\\\hline
  28&TiSapph&Floor\\\hline
  29&Function generator for 1.0 Na switching&Lv1 above TiSapph\\\hline
  30&Keithley power for 1.0 Innolume&Lv2 above TiSapph\\\hline
  31&Till driver v2 for 1.0 Cs MOT&Lv2 above 1.5 Cs MOT\\\hline
  32&Temp servo for 1.0 Cs MOT&Lv2 on Till driver v2\\\hline
  33&Benchtop power 2chn&Lv2 facing computer\\\hline
  34&High voltage power&Above Lv2 on power outlet\\\hline
  \multicolumn{3}{|c|}{1.5 Rack}\\\hline
  35&Home power (24)&Bottom level\\\hline
  36&SEAS pump controller&Middle left\\\hline
  37&Benchtop power&Middle next to pump controller\\\hline
  38&Oscilloscope for 1.5 monitor&Above pump controller\\\hline
  39&Benchtop power 2chn for 1.5 coil&Above oscilloscope\\\hline
  40&High voltage Amp for 1.5 MOT piezo&Top level\\\hline
  41&Function generator for 1.5 MOT piezo&Top level on high voltage Amp\\\hline
  \multicolumn{3}{|c|}{Below 1.5 table}\\\hline
  42&Benchtop power x3&Near outer edge\\\hline
  43&IGBT stack&Floor\\\hline
  44&LED driver&Near inner edge\\\hline
  45&AWG computer&Floor\\\hline
  \multicolumn{3}{|c|}{Above 1.5 table}\\\hline
  46&Benchtop power&Lv1\\\hline
  47&Benchtop power&Lv2\\\hline
  48&Radio computer&Lv2\\\hline
\end{longtable}
\twocolumn

\subsection{Equipments}
\DevDef{Current servo for compensation coil [5]}{
  \textbf{Lv1 below home power (24)}\\
}

\DevDef{Kenneth servo for 1.0 Cs tweezer [6]}{
  \textbf{Lv1}\\
}

\DevDef{High voltage Amp for 630 lock [7]}{
  \textbf{Lv1}\\
}

\DevDef{Vincent servo x2 for STIRAP lasers [8]}{
  \textbf{Lv1}\\
}

\DevDef{Greiner servo for 1.0 Na tweezer [9]}{
  \textbf{Lv1 above Vincent servos}\\
}

\DevDef{Rack for STRAP [10]}{
  \textbf{Lv1 next to Vincent servos}\\
}

\DevDef{Till driver v2 x2 for STIRAP lasers [11]}{
  \textbf{Lv1 above rack for 1.5}\\
}

\DevDef{Temp servo x3 for STIRAP [12]}{
  \textbf{Lv2 next to 9x benchtop power}\\
}

\DevDef{FPGA box for 1.5 [13]}{
  \textbf{Lv2}\\
}

\DevDef{Till driver v2 x2 for 1.5 Cs Raman [18]}{
  \textbf{Floor rack Lv2}\\
}

@@

\DevDef{Temp servo x2 for 1.5 Cs Raman [21]}{
  \textbf{Floor rack Lv2}\\
}

@@

\DevDef{Delay generator for 1.5 Na [23]}{
  \textbf{Lv1 below 1.5 output panel}\\
}

\DevDef{Till driver v2 for 1.0 Innolume [24]}{
  \textbf{Lv1 next to delay generator}\\
}

\DevDef{Kenneth servo for 1.5 tweezers [25]}{
  \textbf{Lv1}\\
}

\DevDef{Temp servo for 1.0 Innolume [26]}{
  \textbf{Lv1}\\
}

\DevDef{Shutter driver [27]}{
  \textbf{Lv1 on M2 controller}\\
}

\DevDef{TiSapph [28]}{
  \textbf{Floor}\\
}

\DevDef{Function generator for 1.0 Na switching [29]}{
  \textbf{Lv1 above TiSapph}\\
}

\DevDef{Keithley power for 1.0 Innolume [30]}{
  \textbf{Lv2 above TiSapph}\\
}

\DevDef{Till driver v2 for 1.0 Cs MOT [31]}{
  \textbf{Lv2 above 1.5 Cs MOT}\\
}

\DevDef{Temp servo for 1.0 Cs MOT [32]}{
  \textbf{Lv2 on Till driver v2}\\
}

\DevDef{SEAS pump controller [36]}{
  \textbf{Middle left}\\
}

\DevDef{Oscilloscope for 1.5 monitor [38]}{
  \textbf{Above pump controller}\\
}

@@

\DevDef{Function generator for 1.5 MOT piezo [41]}{
  \textbf{Top level on high voltage Amp}\\
}

@@

\DevDef{TiSapph}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off pump, unplug from wall
  \item\OffBox Turn off controller, unplug from wall
  \item\OffBox Turn off chiller, unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into wall, turn on chiller
  \item\OnBox Plug into wall, turn on controller
  \item\OnBox Plug into wall, turn on pump
  \end{itemize}
}
\DevDef{Quantel Laser}{
  \textbf{1st level in the middle, facing 1.5 table}\\
  Ask Frederic.
  \vspace{1cm}
}
\DevDef{Intensity servo for Na}{
  \textbf{1st level above Na tweezer, below 1.0 computer control box}\\
  Unplug power
}
\DevDef{1st version Till's current controller for butterfly laser}{
  \textbf{1st level above TiSapph}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power (zip tie to controller)
  \end{itemize}
}
\DevDef{Homebuilt temperature servo for butterfly laser}{
  \textbf{1st level above TiSapph}\\
  Switch off/on the front switch
}
\subsection{Power supplies}
\DevDef{Benchtop power 2chn [1]}{
  \textbf{Lv2}\\
}

\DevDef{Home power (24) [2]}{
  \textbf{Lv2 above 1.0 tweezer breadboard}\\
}

\DevDef{Home power ($\pm$15,5) [3]}{
  \textbf{Lv2 above home power (24)}\\
}

\DevDef{Benchtop power x9 (2chn x3) [4]}{
  \textbf{Lv2 next to home power (24) and ($\pm$15,5)}\\
}

\DevDef{Home power ($\pm$15,5) [14]}{
  \textbf{Lv2 next to FPGA box}\\
}

\DevDef{Benchtop power x2 [15]}{
  \textbf{Lv2 on home power ($\pm$15,5)}\\
}

\DevDef{Benchtop power [16]}{
  \textbf{Lv2 next to home power ($\pm$15,5)}\\
}

\DevDef{Benchtop power x2 (2chn x1) [17]}{
  \textbf{Floor rack Lv1}\\
}

\DevDef{Benchtop power [20]}{
  \textbf{Floor rack Lv2 next to Till drivers}\\
}

\DevDef{Benchtop power 2chn [33]}{
  \textbf{Lv2 facing computer}\\
}

@@

\DevDef{Home power (24) [35]}{
  \textbf{Bottom level}\\
}

\DevDef{Benchtop power [37]}{
  \textbf{Middle next to pump controller}\\
}

\DevDef{Benchtop power 2chn for 1.5 coil [39]}{
  \textbf{Above oscilloscope}\\
}

\DevDef{Benchtop power x3 [42]}{
  \textbf{Near outer edge}\\
}

\DevDef{Benchtop power [46]}{
  \textbf{Lv1}\\
}

\DevDef{Benchtop power [47]}{
  \textbf{Lv2}\\
}

\DevDef{Homebuilt $24$V power supply}{
  \textbf{2nd level above NaCs 1.0 chamber, facing the drawers/wall}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug load
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Switch off on the back
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Switch on
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Benchtop power supply for dispensers}{
  \textbf{1st level above NaCs 1.0 chamber}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Benchtop power supply for 1.5 computer control clock}{
  \textbf{2nd level next to 1.5 computer control box}\\
  Record voltage/current values:\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Homebuilt $\pm15,5$V power supply}{
  \textbf{2nd level above TiSapph}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug load
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Switch off on the back
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Switch on
  \item\OnBox Plug the load back in
  \end{itemize}
}
\subsection{Computers}
\DevDef{AWG computer [45]}{
  \textbf{Floor}\\
}

\DevDef{Radio computer [48]}{
  \textbf{Lv2}\\
}

\DevDef{Computer control box for 1.5}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox (Do following three steps quickly)
  \item\OffBox Turn off the box by flipping the switch on the front side of the box
  \item\OffBox Unplug the high voltage (48V) power supply (circular plug)
    on the left side of the box. Then unplug the power supply itself fromm the outlet.
  \item\OffBox Unplug the 12V board power supply.
    (L.T.E. one with a rectangular connector in the front)
  \item\OffBox Unplug USB power on the front side near the fan.
  \item\OffBox Zip tie the three unpluged powers to the computer control box.
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Connect to 3.5G Windfrek clock generator from Tweezer1.
    Set frequency to 3.5G and amplitude to max.
  \item\OnBox (Remove power connection zip ties and) Plug in USB power supply.
  \item\OnBox (Do following three steps quickly)
  \item\OnBox Plug in the 12V board power supply.
  \item\OnBox Plug in high voltage power supply. The fans should start spinning.
  \item\OnBox Turn on the power switch of the box.
  \end{itemize}
}

>>>>

Please check to make sure the temperature controller for a laser is not turned off before
the laser itself is. If a temperature controller is powered by homebuilt power supply,
mark the output so that it won't be unplugged from the power supply and plug the whole
power supply into the UPS instead of turning off.
Homebuilt power supplies on the UPS should still be switched off if there's no load on it
that needs to be on to reduce load on the UPS/external power.\\

For machine table and 1.5 table, use a normal power strip to collect devices that
needs to be on the UPS. We'll plug the power strip into an actual UPS after the computer
is shut down and the UPS's are freed up.\\

All numbering are from bottom to top and from left to right.\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\subsection{Computers}
\DevDef{Radio computer [3]}{
  \textbf{Lv2}\\
  Ask Yichao
}

@@

\onecolumn
\Person{Jessie and Lewis}{
  Equipments and power supplies are mostly located between the machine table and the 1.5 table.
}
\begin{center}
  {\LARGE\textbf{Equipment list}}
\end{center}
\begin{longtable}{|c|c|c|}
  \hline
  \textbf{ID}&\textbf{Equipment}&\textbf{Location}\\\hline
  \multicolumn{3}{|c|}{\textbf{Machine table Facing the wall} north}\\\hline
  1&Benchtop power 2chn&Lv2\\\hline
  2&Home power (24)&Lv2 above 1.0 tweezer breadboard\\\hline
  3&Home power ($\pm$15,5)&Lv2 above home power (24)\\\hline
  4&Benchtop power x9 (2chn x3)&Lv2 next to home power (24) and ($\pm$15,5)\\\hline
  5&Current servo for compensation coil&Lv1 below home power (24)\\\hline
  6&Kenneth servo for 1.0 Cs tweezer&Lv1\\\hline
  7&High voltage Amp for 630 lock&Lv1\\\hline
  8&Vincent servo x2 for STIRAP lasers&Lv1\\\hline
  9&Greiner servo for 1.0 Na tweezer&Lv1 above Vincent servos\\\hline
  10&Rack for STRAP&Lv1 next to Vincent servos\\\hline
  11&Till driver v2 x2 for STIRAP lasers&Lv1 above rack for 1.5\\\hline
  12&Temp servo x3 for STIRAP&Lv2 next to 9x benchtop power\\\hline
  13&FPGA box for 1.5&Lv2\\\hline
  14&Home power ($\pm$15,5)&Lv2 next to FPGA box\\\hline
  15&Benchtop power x2&Lv2 on home power ($\pm$15,5)\\\hline
  16&Benchtop power&Lv2 next to home power ($\pm$15,5)\\\hline
  17&Benchtop power x2 (2chn x1)&Floor rack Lv1\\\hline
  18&Till driver v2 x2 for 1.5 Cs Raman&Floor rack Lv2\\\hline
  19&Kenneth servo for 1.5 Cs Raman phase lock&Floor rack Lv2 above Till drivers\\\hline
  20&Benchtop power&Floor rack Lv2 next to Till drivers\\\hline
  21&Temp servo x2 for 1.5 Cs Raman&Floor rack Lv2\\\hline
  22&Piezo driver for 1.5 Cs Raman&Floor rack Lv2 above home temp servos\\\hline
  23&Delay generator for 1.5 Na&Lv1 below 1.5 output panel\\\hline
  24&Till driver v2 for 1.0 Innolume&Lv1 next to delay generator\\\hline
  25&Kenneth servo for 1.5 tweezers&Lv1\\\hline
  26&Temp servo for 1.0 Innolume&Lv1\\\hline
  27&Shutter driver&Lv1 on M2 controller\\\hline
  28&TiSapph&Floor\\\hline
  29&Function generator for 1.0 Na switching&Lv1 above TiSapph\\\hline
  30&Keithley power for 1.0 Innolume&Lv2 above TiSapph\\\hline
  31&Till driver v2 for 1.0 Cs MOT&Lv2 above 1.5 Cs MOT\\\hline
  32&Temp servo for 1.0 Cs MOT&Lv2 on Till driver v2\\\hline
  33&Benchtop power 2chn&Lv2 facing computer\\\hline
  34&High voltage power&Above Lv2 on power outlet\\\hline
  \multicolumn{3}{|c|}{1.5 Rack}\\\hline
  35&Home power (24)&Bottom level\\\hline
  36&SAES pump controller&Middle left\\\hline
  37&Benchtop power&Middle next to pump controller\\\hline
  38&Oscilloscope for 1.5 monitor&Above pump controller\\\hline
  39&Benchtop power 2chn for 1.5 coil&Above oscilloscope\\\hline
  40&High voltage Amp for 1.5 MOT piezo&Top level\\\hline
  41&Function generator for 1.5 MOT piezo&Top level on high voltage Amp\\\hline
  \multicolumn{3}{|c|}{Below 1.5 table}\\\hline
  42&Benchtop power x3&Near outer edge\\\hline
  43&IGBT stack&Floor\\\hline
  44&LED driver&Near inner edge\\\hline
  45&AWG computer&Floor\\\hline
  \multicolumn{3}{|c|}{Above 1.5 table}\\\hline
  46&Benchtop power&Lv1\\\hline
  47&Benchtop power&Lv2\\\hline
  48&Radio computer&Lv2\\\hline
\end{longtable}
\twocolumn

\subsection{Equipments}
\DevDef{Current servo for compensation coil [5]}{
  \textbf{Lv1 below home power (24)}\\
  Ask Lewis\\
}

\DevDef{High voltage Amp for 630 lock [7]}{
  \textbf{Lv1}\\
  Ask Lewis\\
}

\DevDef{Vincent servo x2 for STIRAP lasers [8]}{
  \textbf{Lv1}\\
  Ask Lewis\\
}

\DevDef{Rack for STRAP [10]}{
  \textbf{Lv1 next to Vincent servos}\\
  Ask Lewis\\
}

\DevDef{Till driver v2 x2 for STIRAP lasers [11]}{
  \textbf{Lv1 above rack for 1.5}\\
  Record current values:\\

  \begin{tabular}{|c|c|}
    \hline
    No. 1 Current&\hphantom{\hspace{3.5cm}}\\\hline
    No. 2 Current&\\\hline
  \end{tabular}\\

  Ask Lewis\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power (zip tie to controller)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Turn on
  \end{itemize}
}

\DevDef{Temp servo x3 for STIRAP [12]}{
  \textbf{Lv2 next to 9x benchtop power}\\

  Ask Lewis\\
  Check plugged into UPS.
}

\DevDef{Till driver v2 x2 for 1.5 Cs Raman [18]}{
  \textbf{Floor rack Lv2}\\
  Record current values:\\

  \begin{tabular}{|c|c|}
    \hline
    No. 1 Current&\hphantom{\hspace{3.5cm}}\\\hline
    No. 2 Current&\\\hline
  \end{tabular}\\

@@

\DevDef{Temp servo x2 for 1.5 Cs Raman [21]}{
  \textbf{Floor rack Lv2}\\
  Check plugged into UPS.
}

@@

\DevDef{Delay generator for 1.5 Na [23]}{
  \textbf{Lv1 below 1.5 output panel}\\
  Record current values:\\

  \begin{tabular}{|c|c|}
    \hline
    \hphantom{\hspace{3.5cm}}&\hphantom{\hspace{3.5cm}}\\\hline
    &\\\hline
    &\\\hline
    &\\\hline
  \end{tabular}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox
  \item\OffBox
  \item\OffBox
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox
  \item\OnBox
  \item\OnBox
  \end{itemize}
}

\DevDef{Till driver v2 for 1.0 Innolume [24]}{
  \textbf{Lv1 next to delay generator}\\
  Record current values:\\

\DevDef{Temp servo for 1.0 Innolume [26]}{
  \textbf{Lv1}\\
  Check plugged into UPS.
}

\DevDef{Shutter driver [27]}{
  \textbf{Lv1 on M2 controller}\\
  Switch off/on with the switch on the back.
}

\DevDef{TiSapph [28]}{
  \textbf{Floor}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off pump, unplug from wall
  \item\OffBox Turn off controller, unplug from wall
  \item\OffBox Turn off chiller, unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into wall, turn on chiller
  \item\OnBox Plug into wall, turn on controller
  \item\OnBox Plug into wall, turn on pump
  \end{itemize}
}

\DevDef{Function generator for 1.0 Na switching [29]}{
  \textbf{Lv1 above TiSapph}\\
  Record High, Low, Frequency, Phase, Duty cycle\\

  \begin{tabular}{|c|c|}
    \hline
    No. 1 High V&\hphantom{\hspace{3.5cm}}\\\hline
    No. 1 Low V&\\\hline
    No. 1 Frequency&\\\hline
    No. 1 Phase&\\\hline
    No. 1 Duty cycle&\\\hline
    No. 2 High V&\hphantom{\hspace{3.5cm}}\\\hline
    No. 2 Low V&\\\hline
    No. 2 Frequency&\\\hline
    No. 2 Phase&\\\hline
    No. 2 Duty cycle&\\\hline
  \end{tabular}\\
}

\DevDef{Keithley power for 1.0 Innolume [30]}{
  \textbf{Lv2 above TiSapph}\\
  Record voltage/current values:\\

  Turn off after the Innolume is off.
}

\DevDef{Till driver v2 for 1.0 Cs MOT [31]}{
  \textbf{Lv2 above 1.5 Cs MOT}\\
  Record current values:\\

\DevDef{Temp servo for 1.0 Cs MOT [32]}{
  \textbf{Lv2 on Till driver v2}\\
  Check plugged into UPS.
}

\DevDef{SAES pump controller [36]}{
  \textbf{Middle left}\\

\DevDef{Oscilloscope for 1.5 monitor [38]}{
  \textbf{Above pump controller}\\

@@

\DevDef{Function generator for 1.5 MOT piezo [41]}{
  \textbf{Top level on high voltage Amp}\\

  1.0 turn off procedure for reference:\\
  \textbf{Turn on-off together with the HV amplifiers for 1.0 piezo mirrors above
    and the high voltage power supply on the left}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off the function generator
  \item\OffBox Unplug function generator output (zip tie and label)
  \item\OffBox Unplug HV power supply from the wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plugin HV power supply to the wall
  \item\OnBox Plugin function generator output
  \item\OnBox Turn on the function generator
  \end{itemize}
}

@@

\subsection{Power supplies}
\DevDef{Benchtop power 2chn [1]}{
  \textbf{Lv2}\\
  Record voltage/current values:\\

\DevDef{Home power (24) [2]}{
  \textbf{Lv2 above 1.0 tweezer breadboard}\\

\DevDef{Home power ($\pm$15,5) [3]}{
  \textbf{Lv2 above home power (24)}\\

\DevDef{Benchtop power x9 (2chn x3) [4]}{
  \textbf{Lv2 next to home power (24) and ($\pm$15,5)}\\
  Record voltage/current values:\\

  \begin{tabular}{|c|c|}
    \hline
    \small{No. 1 Voltage/Current}&\hphantom{\hspace{4.5cm}}\\\hline
    \small{No. 2 Left Voltage/Current}&\\\hline
    \small{No. 2 Right Voltage/Current}&\\\hline
    \small{No. 3 Voltage/Current}&\\\hline
    \small{No. 4 Voltage/Current}&\\\hline
    \small{No. 5 Left Voltage/Current}&\\\hline
    \small{No. 5 Right Voltage/Current}&\\\hline
    \small{No. 6 Left Voltage/Current}&\\\hline
    \small{No. 6 Right Voltage/Current}&\\\hline
    \small{No. 7 Voltage/Current}&\\\hline
    \small{No. 8 Voltage/Current}&\\\hline
    \small{No. 9 Voltage/Current}&\\\hline
  \end{tabular}\\

\DevDef{Home power ($\pm$15,5) [14]}{
  \textbf{Lv2 next to FPGA box}\\

\DevDef{Benchtop power x2 [15]}{
  \textbf{Lv2 on home power ($\pm$15,5)}\\
  Record voltage/current values:\\

\DevDef{Benchtop power [16]}{
  \textbf{Lv2 next to home power ($\pm$15,5)}\\
  Record voltage/current values:\\

\DevDef{Benchtop power x2 (2chn x1) [17]}{
  \textbf{Floor rack Lv1}\\
  Record voltage/current values:\\

\DevDef{Benchtop power [20]}{
  \textbf{Floor rack Lv2 next to Till drivers}\\
  Record voltage/current values:\\

\DevDef{Benchtop power 2chn [33]}{
  \textbf{Lv2 facing computer}\\
  Record voltage/current values:\\

@@

\DevDef{Home power (24) [35]}{
  \textbf{Bottom level}\\

\DevDef{Benchtop power [37]}{
  \textbf{Middle next to pump controller}\\
  Record voltage/current values:\\

@@

\DevDef{Benchtop power 2chn for 1.5 coil [39]}{
  \textbf{Above oscilloscope}\\
  Record voltage/current values:\\

\DevDef{Benchtop power x3 [42]}{
  \textbf{Near outer edge}\\
  Record voltage/current values:\\

  May need to be adjusted for the uWave Amp.\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}

\DevDef{Benchtop power [46]}{
  \textbf{Lv1}\\
  Record voltage/current values:\\

\DevDef{Benchtop power [47]}{
  \textbf{Lv2}\\
  Record voltage/current values:\\

\subsection{Computers}
\DevDef{Control computers}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Check update.
  \item\OffBox Turn off.
  \item\OffBox Unplug from UPS.
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Get UPS back
  \item\OnBox Turn on.
  \end{itemize}
}
\DevDef{FPGA box for 1.5 [13]}{
  \textbf{Lv2}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox (Do following three steps quickly)
  \item\OffBox Turn off the box by flipping the switch on the front side of the box
  \item\OffBox Unplug the high voltage (48V) power supply (circular plug)
    on the left side of the box. Then unplug the power supply itself fromm the outlet.
  \item\OffBox Unplug the 12V board power supply.
    (L.T.E. one with a rectangular connector in the front)
  \item\OffBox Unplug USB power on the front side near the fan.
  \item\OffBox Zip tie the three unpluged powers to the computer control box.
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Connect to 3.5G Windfrek clock generator from Tweezer1.
    Set frequency to 3.5G and amplitude to max.
  \item\OnBox (Remove power connection zip ties and) Plug in USB power supply.
  \item\OnBox (Do following three steps quickly)
  \item\OnBox Plug in the 12V board power supply.
  \item\OnBox Plug in high voltage power supply. The fans should start spinning.
  \item\OnBox Turn on the power switch of the box.
  \end{itemize}
}
\DevDef{AWG computer [45]}{
  \textbf{Floor}\\
  Ask Yichao
}
\DevDef{Radio computer [48]}{
  \textbf{Lv2}\\
  Ask Yichao
}
